Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-09 writing/embedded_meta_learning.tex
Repo links

\section{Card game $t$-SNE} \label{app_cards_tsne}
We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network. In fig. \ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks. The embeddings show systematic grouping by game attributes. In fig. \ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type. \par 
\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks. (Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)} 
\label{fig_cards_tsne_basic}
\end{figure}%
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
\label{fig_cards_tsne_full}
\end{figure}

>>>>

\subsection{Model \& training}
See table \ref{supp_hyperparameter_table} for detailed architectural description and hyperparameters for each experiment. Hyperparameters were generally found by a heuristic search, where mostly only the optimizer, learning rate annealing schedule, and number of training epochs were varied, not the architectural parameters. Some of the parameters take the values they do for fairly arbitrary reasons, e.g. the continual learning experiments were run with the current polynomial hyperparameters before the hyperparameter search for the polynomial data was complete, so some parameters are altered between these. \par
Each epoch consisted of a separate learning step on each task (both base and meta), in a random order. The embeddings of the tasks for the meta-learner were computed once per epoch, so as the network learned over the course of the epoch, the 
\begin{table}[H]
\begin{tabular}{|c|ccc|}
\hline 
& \phantom{bla}Polynomials\phantom{la} & Continual learning & \phantom{blahb}Cards\phantom{blahb} \\
\hline
$Z$-dimension & 512 & 512 & 512 \\
$\mathcal{I}$ num. layers & \multicolumn{3}{c|}{3} \\ 
$\mathcal{I}$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
$\mathcal{O}$ num. layers & 1 & 1 & 3 \\ 
$\mathcal{O}$ num. hidden units & - & - & 512 \\ 
$\mathcal{T}$ num. layers & \multicolumn{3}{c|}{1} \\ 
$\mathcal{M}$ architecture & \multicolumn{3}{c|}{2 layers per-datum, max pool across, 2 layers} \\ 
$\mathcal{H}$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
$\mathcal{M}, \mathcal{H}$ num. hidden units & \multicolumn{3}{c|}{512} \\ 
$f$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
$f$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
Nonlinearities & \multicolumn{3}{c|}{Leaky ReLU, no non-linearity at final layer of $T$, $M$, $f$.} \\
\hline
Optimizer & Adam & RMSProp & RMSProp \\
Learning rate (base) & $3\cdot 10^{-5}$ & $1\cdot 10^{-4}$ & $1\cdot 10^{-4}$\\
Learning rate (meta) & $1\cdot 10^{-5}$ & - & $1\cdot 10^{-4}$\\
L.R. decay rate (base) & $*0.85$ & $*0.85$ & $*0.85$ \\
L.R. decay rate (meta) & $*0.85$ & - & $*0.9$ \\
L.R. min (base) & \multicolumn{3}{c|}{$3 \cdot 10^{-8}$} \\
L.R. min (meta) & $1 \cdot 10^{-7}$& - & $3 \cdot 10^{-7}$ \\
L.R. decays every & \multicolumn{3}{c|}{$100$ epochs if above min.} \\
Cached embedding L.R. & - & $1\cdot 10^{-3}$ & -\\
Num. training epochs & 4000 & 3000 & 40000 \\
\hline
Num. base tasks (eval) & 60 & 100 & 36 or 20 \\
Num. base tasks (training) & 1200 (= 60 * 20) & 100 & 36 or 20  \\
Num. meta classifications & 6 & - & 8  \\
Num. meta mappings & 20 & - & 3  \\
Num. new base tasks & 40 & 30 & 4 or 20 \\ 
Num. new meta mappings & 16 & - & 0  \\
Num. new meta classifications &  \multicolumn{3}{c|}{0} \\
Base dataset size & \multicolumn{3}{c|}{1024} \\
Base datasets refreshed & \multicolumn{3}{c|}{Every 50 epochs} \\
$\mathcal{M}$ batch size & 50 & 128 & 768 \\
\hline
\end{tabular}
\caption{Detailed hyperparameter specification for different experiments. A ``-'' indicates a parameter that does not apply to that experiment. Where only one value is given, it applied to all the experiments discussed. As a reminder: the shared representational space is denoted by $Z$. Input encoder: $\mathcal{I}: \text{input} \rightarrow Z$. Output decoder $\mathcal{O}: Z \rightarrow \text{output}$. Target encoder $\mathcal{T}: \text{targets} \rightarrow Z$. Meta-network $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- takes a set of (input embedding, target embedding) pairs and produces a function embedding. Hyper-network $\mathcal{h}: Z \rightarrow \text{parameters}$ -- takes a function embedding and produces a set of parameters. Task network $f: Z \rightarrow Z$ -- the transformation that executes the task mapping, implemented by a deep network with parameters specified by $\mathcal{H}$.} \label{supp_hyperparameter_table}
\end{table}
\subsection{Source repositories}
The full code can be found on github:
\begin{itemize}
\item \url{https://github.com/lampinen/polynomials}
    \begin{itemize}
        \item See the continual\_learning branch for those results. 
    \end{itemize}
\item \url{https://github.com/lampinen/meta_cards} 
\end{itemize}
%%(will be made available in the de-anonymized version.)
\section{Card game $t$-SNE} \label{app_cards_tsne}
We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network. In fig. \ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks. The embeddings show systematic grouping by game attributes. In fig. \ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type. \par 
\begin{figure}[H]
\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks. (Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)} 
\label{fig_cards_tsne_basic}
\end{figure}%
\begin{figure}[H]
\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
\label{fig_cards_tsne_full}
